\begin{description}
	\item[Game Arena] Player 0: Circle, Player 1: Square, environment, bad.
	\item[Winning Condition] Set of traces.
	\begin{itemize}
		\item Reachability Game
		\item Safety Game (Reachability with reversed player roles)
		\item Büchi Game
		\item Parity Game
	\end{itemize}
	\item[Controllable Pre-Operator] \ 
	\begin{align*} 
	\CPRE_i(S) = &\{ v \in V_i | \exists v' \in V. (v,v') \in E \land v' \in S \} \\
	&\cup \{ v \in V_{1-i} | \forall v' \in V. (v, v') \in E \implies v' \in S \}
	\end{align*}
	\ie, any position where we can enforce to end up in $S$.
	\item[Attractor construction] For reachability games:
	\begin{align*}
		\ATTR^0_i(R) &= R \\
		\ATTR^{n+1}_i(R) &= \ATTR_i^n(R) \cup \CPRE_i(\ATTR_i^n(R))\\
		\ATTR_i(R) &= \bigcup_{n \in \mathds{N}} \ATTR_i^n(R)
	\end{align*}
	Therefore, $\ATTR_i^n(R)$ means that player $i$ can reach $R$ in at most $n$ steps.
	\item[Recurrence Construction] For Büchi games. $\RECUR^n(F)$ means that player 0 can enforce to come back to $F$ at least $n$ \emph{additional} times.
	\begin{align*}
		W_0 &= \ATTR_0(\RECUR(F))\\
		W_1 &= V\BS W_0\\
		\RECUR^0(F) &= F\\
		W_1^n(F) &= V\BS \ATTR_0(\RECUR^n(F))\\
		\RECUR^{n+1}(F) &= \RECUR^n(F)\BS \CPRE_1(W_1^n(F))\\
		\RECUR(F) &= \bigcap_{n \in \mathds{N}} \RECUR^n(F)
	\end{align*}
	\item[Extracting the winning strategy] Always move to the attractor level with the least reachable $n$.
	\item[Synthesis from LTL] 
	\begin{enumerate}
		\item LTL Specification
		\item Deterministic Automaton
		\item Game
		\item Check winner. If player 0 wins, the specification is realizable.
	\end{enumerate}
	\item[Transforming Automata to Games] \ 
	\begin{itemize}
		\item Given a state $s$, with inputs $I$ and outputs $O$. 
		\item Introduce position for player 1 named $s, o$ where o is the output in state s. 
		\item For each possible input $i$ introduce a position for player 0 named $s, o, i$ meaning that the output remains the same, the input came from the environment. 
		\item For each possible reaction to this input, introduce another position representing this actions.
	\end{itemize}
	\item[Parity Games] 
	\[ \textit{Parity}(\Omega) = \{ p_0p_1\ldots \in V^\omega | \min\{ n \in \mathds{N} | \forall i \exists j. j>i \land \Omega(p_j) = n \} \text{ is even} \} \] 
	That means, the minimal color that is visited infinitely often is even.
\end{description}

\subsection{Timed Games}

\begin{itemize}
	\item Player 0 chooses action and delay $t \geq 0$. During this delay, state invariants must not be violated.
	\item Player 1 either accepts Player 0's choice or chooses a delay $\leq t$ and an \textbf{uncontrollable} action which guard is satisfied.
	\item Controllable predecessors $P$ are states with respective time intervals such that Player 1 cannot make Player 0 leave $P$ without reaching the desired state.
\end{itemize}

\subsection{Abstractions}
\begin{itemize}
	\item Use an abstraction to obtain a discrete model via partitioning. 
	\item Either all or no state in an element of the partition satisfy any given property.
	\item Abstract transitions must be realizable in the continuous world.
	\item Use a discrete planner to obtain a discrete plan.
	\item The continuous planner transforms this plan into an applicable plan for the real world.
\end{itemize}

\subsection{Receding Horizon}

\begin{itemize}
	\item Define partial order on state partition with $W_0$ is minimum.
	\item All goals are in $W_0$.
	\item Define a synthesis-strategy function $F$ agreeing with the order. 
	\item $F(W) = W'$ means that we synthesize a strategy from $W$ to $W'$.
	\item After reaching $W'$ we keep synthesizing towards $W_0$.
	\item Define invariant that holds in the initial states.
\end{itemize}


