\subsection{Basic Terminology}
\begin{description}
	\item[Release Time $r_i$ (aperiodic tasks)]
	\item[Computation Time $C_i$]
	\item[Deadline $d_i$]
	\item[Slack time $X_i$] = $d_i - r_i - C_i$ max time that can pass until
	this task \textbf{must} be scheduled.
	\item[Laxity] deadline - remaining computation time
	\item[Start Time $s_i$]
	\item[Finishing Time $f_i$]
	\item[Lateness $L_i$] = $f_i - d_i$
	\item[Exceeding Time $E_i$] = $\max(0, L_i)$
	\item[Phase $\Phi_i$] time before the periodic task arrives for the first
	time.
	\item[Period $T_i$] time between consecutive arrivals of a periodic task.
	\item[Relative Deadline $D_i$] Time from release time to respective deadline.
	\item[Release Time (periodic tasks)] In $k$th period: $\Phi_i + k T_i$
	(starting with 0th period).
	\item[Synchronous] $\forall i: \ r_i = 0$
	\item[Independent] No predecessor relation; task can be scheduled in any
	order.
	\item[Shared Resource] Can be used by multiple processes (at once)
	\item[Mutually Exclusive Resource]Can be used by multiple processes one
	after each other.
	\item[Critical Section] Mutex code.
	\item[Semaphore] Operations \texttt{wait} and \texttt{signal}
	\item[Preemptive] \textit{Can} be interrupted.
	\item[Feasible Schedule] Can be executed without violating specified
	properties (\eg not missing deadlines).
\end{description}

\subsection{Cost Functions}
\begin{description}
	\item[Avg Response Time] \ 
	\[ \bar{t_r} = \frac{1}{n}\sum_{i=1}^n(f_i-r_i) \]
	\item[Total Completion Time] \ 
	\[ t_c = \max_i(f_i) - \min_i(r_i) \]
	\item[Weighted Sum of Response Times]\ 
	\[ t_w = \frac{1}{n}\sum_{i=1}^nw_i(f_i-r_i) \]
	\item[Maximum Lateness] \ 
	\[ L_{\max} = \max_i(f_i - d_i) \]
	\item[Number of Late Tasks] \ 
	\[ N_{\text{late}} = \sum_{i=1}^n \INDICATOR{f_i > d_i} \]
\end{description}

\subsection{Aperiodic Scheduling}
\begin{description}
	\item[EDD - Earliest Due Date] Synchronous, independent tasks. Preemption
	does not matter. \\ Complete, minimizes maximum lateness.\\ $\in \BIGO(n
	\log n)$
	\item[EDD without preemption] Optimal iff non-idle
	\item[EDF - Earliest Deadline First] Aperiodic, preemptive.\\ Complete,
	minimizes maximum lateness.\\ $\in \BIGO(n \log n)$, when $k$ tasks arrive,
	additionally $\BIGO(k*n)$
	\item[EDF with Dependent Tasks] Choose earliest deadline among all sources,
	schedule, remove, repeat. \textbf{Not} optimal
	\item[EDF*] Optimal for preemptive, asynchronous scheduling.\\
	Either modify the deadlines of all non-sinks:
	\[ d_i^* = \min(d_i, \min\{d_j^* - C_j : J_i \text{ depends on } J_j\}) \]
	Or modify the release time of all non-sources
	\[ r_j^* = \max(r_j, \max\{r_i^* + C_i : J_i \text{ depends on } J_j\}) \]
	\item[LDF with Dependent Tasks] Choose latest deadline among all sinks,
	schedule, remove, repeat. Optimal. Off-line computable $\in \BIGO(n * \max
	\{|E|, \log n\})$.
	\item[Bratley's algorithm] For each schedulable task: Check whether when
	scheduled another task will miss the deadline. Yes $\rightarrow$ search for
	other schedule. No $\rightarrow$ recursion. \\ 
	Exponential time $\rightarrow$ use off-line.
\end{description}

\subsection{Periodic Scheduling}
\begin{description}
	\item[Processor Utilization] \ 
	\[ U = \sum_{i=1}^n \frac{C_i}{T_i} \]
	\item[Utilization Bound (single processor)] $U < U_{bnd} \rightarrow$
	schedulable.\\
	$U_{bnd} \leq U \leq 1 \rightarrow$ maybe schedulable.\\
	$U > 1 \rightarrow$ not schedulable.
	\item[EDF - Earliest Deadline First] Works, but is too slow for practice.
	$U_{bnd} = 1$ for $D_i \geq T_i$
	\item[RM - Rate Monotonic] Assume $T_i = D_i$. prio$(\tau_i) = T_i^{-1}$.\\
	Optimal among fixed priority schedulers. $U_{bnd} = \ln 2 \approx 0.69$.\\
	Exact check:
	\textbf{Intuitive}
	\begin{enumerate}
		\item Sort by priorities, \ie, $i = 1$ has highest priority.
		\item Initialize: $R^0_i = C_i$
		\item For the job with the highest priority we are done.
		\item For any other job, check current $R^k_i$ value. When this value strictly
		exceeds the period of any other job, account for this job's computation time
		by adding it.
		\item Remember that in the first iteration, we have to take \emph{all} tasks
		with higher priority into account.
	\end{enumerate}
	\textbf{Formal}
	\begin{enumerate}
		\item Sort by priorities, \ie, $i = 1$ has highest priority.
		\item Initialize: $R^0_i = C_i$
		\item Iteration $j$: For each $i > 1$ where $i$ is not a fix-point yet:
			\begin{enumerate}
				\item \ 
				\[ R_i^{j+1} = C_i + \sum_{k=1}^{i-1} C_k \left\lceil \frac{R_i^j}{T_k}
				\right\rceil \]
			\end{enumerate}
		\item Repeat until all $i$s are fix-points.
		\item If any $R_i$ is greater than its $C_i \rightarrow$ not schedulable.
		\item Else: RM-schedulable. 
	\end{enumerate}
	With critical resources see next section.
\end{description}

\subsection{Scheduling with Resources}

\begin{description}
	\item[Priority Inheritance] If job $J_1$ needs a resource held by a lower
	priority job $J_2$, then $J_2$ inherits $J_1$'s priority.
	\item[Direct Blocking] Job blocked by missing resource held by lower priority
	job.
	\item[Push-Through Blocking] Job $J_m$ is blocked by lower priority job $J_l$,
	that blocks higher priority job $J_h$ directly. Therefore, $J_m$ has to wait
	for $J_l$ and $J_h$ to finish.
	\item[Schedulability check] Use 
	\[ R_i^{j+1} = C_i + B_i + \sum_{k=1}^{i-1} C_k \left\lceil \frac{R_i^j}
	{T_k} \right\rceil\]
	instead, where $B_i$ is the maximum blocking time.
	\item[Blocking Time Approximation] $D_{j,k}$: Duration of longest critical
	section of task $\tau_k$ using critical section $S_k$.\\
	Jobs ordered by priority, $n$ tasks, $m$ critical sections.
	\[ B_i \leq \sum_{j = i+1}^n \max_k\{ D_{j,k} | C(S_k) \leq P_i \} \]
	\[ B_i \leq \sum_{k = 1}^m \max_{j>i}\{ D_{j,k} | C(S_k) \leq P_i \} \]
	\item[Exact Blocking Time] Exhaustive search, exponential time.
	\item[Priority Ceiling] $C(S) = \max\{\text{prio}(J)|\text{ J can lock } S \}$
	\item[Priority Ceiling Protocol] J can lock $S$ if its priority is \emph
	{greater} than the \emph{ceilings} of all semaphores locked by other tasks.\\
	If not the case, $J$ gets priority of this very task.\\
	When exiting the critical section, the priority is set to highest priority of a
	job blocked by the exiting job.\\
	When checking whether $J_i$ can lock $S_i$ while $M$ is the set of semaphores that are currently locked, check: 
	\[ \text{prio}(J_i) > \max_M\{C(S)\} \]
\end{description}

\subsection{Multiprocessor Scheduling with preemption}
\begin{description}
	\item[Schedulability] $U \leq n$
	\item[Game Board Representation] x-Axis: Laxity \\
	y-Axis: Remaining computation time
	\item[Least Laxity First] Optimal.
	\item[Fully Run] $FR(t,k) = \{i \in M | D_i(t) \leq k \}$
	\item[Partially Run] $PR(t,k) = \{i \in M | L_i(t) \leq k \land D_i(t) > k \}$
	\item[Need Not Be Run] $NN(t,k) = \{i \in M | L_i(t) > k \}$
	\item[Surplus Computing Power] \ 
	\[ SCP(t,k) = (k * n) - \sum_{i \in FR(t,k)} C_i(t) - \sum_{i \in PR(t,k)} (k -
	L_i(t)) \]
	$SCP(0,k) \geq 0 \forall k > 0$ is a necessary and sufficient condition on
	schedulability.
	\item[Scheduling idea] See slide 14:36, 14:39
	\item[Operating Systems] 14:43, 14:45, 14:46, 14:47, 14:50
\end{description}