\subsection{Black Box Testing}

\begin{description}
	\item[Equivalence Partitioning] Find equivalence classes $E_i$ in input.
	Invalid inputs for (at least) an equivalence class as well. \\ Find test
	cases:
	\begin{itemize}
		\item Pick exactly one input. Choose invalid value for that. For each
		other input, pick valid value.
		\item Pick as many equivalence classes that can be cover at once as
		possible. No invalid values!
	\end{itemize}
	Repeat until each invalid class is covered in isolation, and each valid
	class is covered without any invalid cases in the same test.

	\item[Boundary-Value Analysis] Additionally, test all values that are a
	boundary for an equivalence class.

	\item[Cause-Effect Graphing] Undirected edges, connecting cause and effect,
	annotated by logical \texttt{and}, \texttt{or}, or \texttt{not} (sine wave on
	edge). \\
	Additionally, with dashed lines:\\
	\begin{description}
		\item[Mutually Exclusivity] Connect mutex nodes with an \textbf{E}
		\item[At Least One True] Connect those nodes with an \textbf{I}
		\item[Exactly One True] Connect those nodes with an \textbf{O}
		\item[Reliance] (directed) $a$ can only be true if $b$ is true $\rightarrow$ edge
		from $a$ to $b$ annotated with an \textbf{R}
	\end{description}
	\item[Decision Table] \ 
	\begin{enumerate}
		\item Initialize one row for each cause or effect.
		\item For each effect: 
		\begin{enumerate}
			\item One column for each combination of causes such that effect is 1.
			\item Annotate causes with fixed values or undefined.
			\item Annotate the other effects with the respective desired outcome.
		\end{enumerate}
		\item Each column is a test case, where the input is given by the causes, the
		effect values are the desired results.
		\item Disjunction: Purge cases where both inputs are 1. Consider all others.
		\item Conjunction: Purge cases where both inputs are 0. Consider all others.
	\end{enumerate}
	\item[Error Guessing] Speaks for itself.
\end{description}

\subsection{White Box Testing}
\begin{description}
	\item[Control Flow Graph] Statement nodes: Square, Decision Nodes: Diamond.
	\item[Condition Coverage] For con-/disjunction in decision nodes: Each
	part has to be true and false at least once.
	\item[Condition/Decision Coverage] Condition + Decision coverage.
	\item[Multiple-Condition Coverage] Each combination of condition outcomes must
	be covered.
	\item[Path Coverage] \textbf{every} path needs to be covered.
	\item[Simple Path] No repeated nodes.
	\item[Prime Path] Simple path of maximum length.
	\item[Observability Problem] Internal state hidden $\rightarrow$ probing.
	Problem: Invasive and takes time. Alternative: snooping on bus.
	\item[Reproducibility Problem] Time changes behavior. Run multiple times,
	identify interesting points in time, analyze accordingly.
	\item[Environment Simulation Problem] Real environment costly/risky. Simulation
	not always realistic.
\end{description}

\subsection{Model-based Testing}
\begin{description}
	\item[FSM Initially Connected] Each state reachable from the initial state.
	\item[FSM complete] For each state and input, there is a transition.
	\item[FSM strongly Connected] Every state is reachable from every state.
	\item[Timed Automata] Edge syntax: (A|g)/R means actions A enabled if g holds.
	Application resets R.
	\item[Region Abstraction] Equivalence classes for making clocks integral, so we
	have regions for $x = 0, 0 < x < 1, x = 1, ...$ until it makes no sense
	anymore. Time transitions marked as $\tau$.
	\item[Composition of FSMs] See slide 16:38.
\end{description}

\subsection{LTL, Traces, Property Checking}

\begin{description}
	\item[Bad Prefix] Bad prefix of $\sigma$ is a finite prefix $\hat\sigma$ of
	$\sigma$ where no extension would satisfy a given property.
	\item[Safety] Every infinite trace violating the property has a bad prefix.
	That means, once we were in a bad state, we are lost.
	\item[Check Safety] Express property as automaton, construct composition with
	the model automaton, check reachability of any error state.
	\item[Liveness] Violating traces do not have a bad prefix. That means, we want
	to ensure that something specific happens in the future given certain
	circumstances.
	\item[Safety Monitor] Shipped with a state labeling function. 1 for bad states,
	0 for good ones.
	\item[LTL] \textbf{Eventually:} Now or some time in the future.\\
	\textbf{Until:} $a\textbf{U}b$ holds if $b$ holds from now on forever, or $a$
	holds until $b$ holds forever.
	\item[Büchi Automaton] Accepts if an accepting state is visited infinitely
	often.
	\item[Model Checking with LTL] Check whether $\varphi$ holds: 
	\begin{enumerate}
		\item Negate $\varphi$.
		\item Transform in Büchi Automaton.
		\item Construct composition with model automaton.
		\item Search for reachable loops with accepting states.
		\item If found, there are sequences violating $\varphi$.
	\end{enumerate}
	\item[Zone Graph] Input: Region Graph.
	\begin{enumerate}
		\item Start with initial region. Repeat for each newly created zone.
		\item Collapse zone with all regions reachable by delay transition. 
		\item Add edge to regions (or zones) reachable by discrete transitions.
	\end{enumerate}
	\item[Hybrid Reachability Checking] Assume derivative to be constant
	$\rightarrow$ get regions of potential values
	\item[Linear Hybrid Automate] Guard and invariants are linear equations. Allows
	for exact reachability checks.
\end{description}
