\MAX{include graphic illustrating the four properties for a controller curve}


\subsection{A/D Conversion}
\begin{description}
	\item[CCD Image Sensors] Charge-coupled devices. Sequential charge transfer,
	complex interface, low power consumption.
	\item[CMOS] Complementary metal oxide semiconductor. Cheap, random access,
	simple interface.
	\item[Flash A/D] Compare against $\frac{k}{\alpha} \ \forall k \in [\alpha]$
	in parallel. Speed $\in \BIGO(1)$, cost $\in \BIGO(\alpha)$.
	\item[Successive Approximation] Binary search for closest value. Example:
	Given input $V = 7$, reference value (max value) $V_{ref} = 10$, 3 bit
	precision,
	output $x[2:0]$:
	\begin{itemize}
		\item x[2] = 1 since $7 = V > \frac{1}{2} V_{ref} = 5$
		\item x[1] = 0 since $7 = V \ngtr \frac{3}{4} V_{ref} = 7.5$
		\item x[0] = 1 since $7 = V > \frac{5}{8} V_{ref} = 6.25$
	\end{itemize}
	Speed, cost $\in \BIGO(\log n)$.
\end{description}

\subsection{Sampling}

\begin{description}
	\item[Aliasing] High frequency masquerades as low frequency. \MAX{include
	image example}
	\item[Anti-Aliasing] Use low-pass filter, \ie, forsake high frequency parts
	\quote{smoothing} it into a low frequency wave.
	\item[Nyquist Criterion] $p_N$ period of fastest wave, $f_N$ frequency of
	fastest wave. Aliasing avoidable if sampling period $p_S$ < $\frac{1}{2} p_N$
	and equivalently $f_S$ > 2 $f_N$.
	\item[Fourier Approximation] assume period $p$
	\[ 
	e'_k(t) = \sum^{k}_{i < k \text{ odd}}\frac{4}{\pi i} \sin\left(\frac{2\pi t}
	{p/k}\right)
	\]
	\item[Shannon-Whittaker Interpolation] Consider $y$ to be reconstructed, $S$
	samples $p_s$ at sampling times $t_s$ for $s \in [S]$
	\begin{align*}
	z_y(t) 	&= \sum_{s \in S} y(t_s) * \SINC(t - t_s)\\
	 		&= \sum_{s \in S} y(t_s) * \frac{\sin\left(\frac{\pi}{p_s}(t-t_s)\right)}
	 		{\frac{\pi}{p_s}(t-t_s)}
	\end{align*}
\end{description}

\subsection{Dynamics, Stability \& Controlling}
\begin{description}
	\item[State Dynamics] $\dot{S} = AS + BI, O = CS + DI$
	\item[Input-Output Linearity] For linear components: \\
	\begin{align*}
	I'(t) := \alpha I(t) &\Rightarrow O'(t) = \alpha O(t) \NOTE{(scalability)}\\
	I'(t) := I_1(t) + I_2(t) &\Rightarrow O'(t) = O_1(t) + O_2(t) \NOTE{(additivity)}
	\end{align*}
	\item[Similarity Transformation] Compute $A$'s eigenvalues $\lambda_i$ and
	eigenvectors $v_i$ (see Section \ref{sec:maths}).\nl
	$P := (v_1,\ldots, v_m)$, compute $P^{-1}$. \nl
	$S(t) = PD(e^{\lambda_1t}, \ldots, e^{\lambda_mt})P^{-1} s_0$
	\item[Stability] Eigenvalues' real part:\\
    all negative $\implies$ asymptotically stable\\ 
	all non-negative $\implies$ stable\\
    any positive $\implies$ unstable\\
	$A$ invertible $\implies$ only one equilibrium\\
	$s$ non-zero equilibrium: $S' = S - s \rightarrow$ properties hold for S'. 
	\item[BIBO Stability] implied by asymptotic stability.
	\item[Controllability] \[C[A,B] = \left[ \begin{array}{ccccc}
    B & AB & A^{2}B & \cdots & A^{n-1}B \end{array} \right] \in \mathbb{R}^{n \times nm}\]
    $C[A,B]$ has full rank $\iff$ rows linearly independent $\iff$ system is controllable.
	\item[Stabilization (control)] Reference vector $R$. $\dot{S} = (A - BF)S + BFR$. Find
	$F$ such that eigenvalues of $(A - BF)$ are negative. See remark regarding
	finding negative eigenvalues in Section \ref{sec:maths}.
	\item[Error (control)] Difference between wanted and actual value (reference minus current)
	\item[Rise Time, Overshoot, Settling Time, Steady State error] See illustration
	TODO
	\item[P-Controller] Proportional error, \ie, the current error. $K_P e(t)$
	% \textbf{increases} overshoot, \textbf{decreases} rise time, steady state error,
	% \textbf{no change} on settling time.
	\item[I-Controller] Integral error, \ie, accumulated error so far. $K_I
	\int_0^\tau e(\tau) d\tau$
	\item[D-Controller] Derivative error, \ie, current error's rate of change.
	$K_D \dot{e}(t)$
\end{description}
